---
title: "Cancer"
output: 
  html_document:
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("setup_ubcos.r")
```
<!-- ########################################################## --> 

# Description of DataSchema variable 

Two variables are created: `cancer`and `cancer_age`:

* Short name: `cancer`
* Variable label: `cancer`
* Variable description: `First episode of cancer in the last observed period of time.`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Short name: `cancer_age`
* Variable label: `Age of cancer`
* Variable description: `Age of first episode of cancer in the last observed period of time.`
* Domain: `Diseases`
* Value type: `continuous`

* Category missings in both variables: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not applicable
995 | Does not answer
996 | Not attempt/not done
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label   <- "cancer"
ds_label_a <- "Age of cancer"
c_label    <- c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991)
c_label_a <- c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991)
m_label    <- c("No"=0, "Yes"=1)
```

<!-- ########################################################## --> 

# Data process

## Uppsala 1st generation cohort

### Wave 1

No information was registered.

### Wave 2

#### Study-specific variable description

Two variables are taken from the UBCoS dataset:

* Name: `cancer1970`
* Table name: `ubcosG1W2`
* Description: `First diagnosis of cancer before the 1st November 1970`

```{r f121, echo=FALSE}
sds <- ubcosG1W2[c("athlosid", "cancer_firstdate1970", "cancer_firstage1970", "cancer1970")]

kable(frq(sds[[4]])[[1]])

ggplot(sds, aes(x=as.factor(sds[[4]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)
```

* Name: `cancer_firstage1970`
* Table name: `ubcosG1W2`
* Label: `Age of first diagnosis of cancer before the 1st November 1970`
* Description: 

```{r f122, echo=FALSE}
ssds <- data.frame(sds) #remove tibble format

ggplot(ssds[ssds[,4]==1,], aes(x=ssds[ssds[,4]==1,3],)) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

#### Harmonisation algorithm

For the variable `cancer`, value 0 is assigned when date of first diagnosis of cancer is later than 1st November 1970, the approximate date of the census registry, or never, and value 1 when prior to that date. 

**R script:**
```{r h121}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], cancer=sds[[4]])
```

For the variable `cancer_age`, the same age is assigned when the first diagnosis of cancer is before than 1st November 1970, otherwise the value 994 (not applicable) is assigned.

**R script:**
```{r h122}
# 'sds': study dataset
# 'hds': harmonised dataset
hds$cancer_age <- sds[[3]]
hds[hds$cancer != 1,]$cancer_age <- 994
```

#### Statistical description of the new harmonised variable
```{r d12, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)

hds[[3]] <- labelled(hds[[3]], labels = c_label_a)
ggplot(hds[hds[[3]]<990,], aes(x=hds[hds[[3]]<990,3])) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

<!---###### Validation
```{r v12, echo=FALSE}
#taux <- merge(hds, sds, by.x="id", by.y="athlosid")
#kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```
-->




<!--- ################## Save harmonised datasets ###################-->
```{r s12, echo=FALSE}
load("UBCoS_g1_w2.rdata")
UBCoS_g1_w2 <- full_join(UBCoS_g1_w2, hds, by="id", all=TRUE)
#save(UBCoS_g1_w2, file="UBCoS_g1_w2.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(hds[[2]], labels = m_label)
mds[[3]][mds[[3]] %in% c(991:999)] <- NA
val_labels(mds[[3]]) <- NULL
load("UBCoS_m_g1_w2.rdata")
UBCoS_m_g1_w2 <- full_join(UBCoS_m_g1_w2, mds, by="id", all=TRUE)
#save(UBCoS_m_g1_w2, file="UBCoS_m_g1_w2.rdata")

rm(list = c("hds", "sds", "mds"))
```

### Wave 3

#### Study-specific variable description

Two variables are taken from the UBCoS dataset:

* Name: `cancer1980`
* Table name: `ubcosG1W3`
* Description: `First diagnosis of cancer before the 15th September 1980`

```{r f131, echo=FALSE}
sds <- ubcosG1W3[c("athlosid", "cancer_firstdate1980", "cancer_firstage1980", "cancer1980")]

kable(frq(sds[[4]])[[1]])

ggplot(sds, aes(x=as.factor(sds[[4]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)
```

* Name: `cancer_firstage1980`
* Table name: `ubcosG1W3`
* Label: `Age of first diagnosis of cancer before the 15th September 1980`
* Description: 

```{r f132, echo=FALSE}
ssds <- data.frame(sds) #remove tibble format

ggplot(ssds[ssds[,4]==1,], aes(x=ssds[ssds[,4]==1,3],)) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

#### Harmonisation algorithm

For the variable `cancer`, value 0 is assigned when date of first diagnosis of cancer is later than 15th September 1980, the approximate date of the census registry, or never, and value 1 when prior to that date. 

**R script:**
```{r h131}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], cancer=sds[[4]])
```

For the variable `cancer_age`, the same age is assigned when the first diagnosis of cancer is before than 15th September 1980, otherwise the value 994 (not applicable) is assigned.

**R script:**
```{r h132}
# 'sds': study dataset
# 'hds': harmonised dataset
hds$cancer_age <- sds[[3]]
hds[hds$cancer != 1,]$cancer_age <- 994
```

#### Statistical description of the new harmonised variable
```{r d13, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)

hds[[3]] <- labelled(hds[[3]], labels = c_label_a)
ggplot(hds[hds[[3]]<990,], aes(x=hds[hds[[3]]<990,3])) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

<!---###### Validation
```{r v13, echo=FALSE}
#taux <- merge(hds, sds, by.x="id", by.y="athlosid")
#kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```
-->




<!--- ################## Save harmonised datasets ###################-->
```{r s13, echo=FALSE}
load("UBCoS_g1_w3.rdata")
UBCoS_g1_w3 <- full_join(UBCoS_g1_w3, hds, by="id", all=TRUE)
#save(UBCoS_g1_w3, file="UBCoS_g1_w3.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(hds[[2]], labels = m_label)
mds[[3]][mds[[3]] %in% c(991:999)] <- NA
val_labels(mds[[3]]) <- NULL
load("UBCoS_m_g1_w3.rdata")
UBCoS_m_g1_w3 <- full_join(UBCoS_m_g1_w3, mds, by="id", all=TRUE)
#save(UBCoS_m_g1_w3, file="UBCoS_m_g1_w3.rdata")

rm(list = c("hds", "sds", "mds"))
```

### Wave 4

#### Study-specific variable description

Two variables are taken from the UBCoS dataset:

* Name: `cancer1990`
* Table name: `ubcosG1W4`
* Description: `First diagnosis of cancer before the 1st November 1990`

```{r f141, echo=FALSE}
sds <- ubcosG1W4[c("athlosid", "cancer_firstdate1990", "cancer_firstage1990", "cancer1990")]

kable(frq(sds[[4]])[[1]])

ggplot(sds, aes(x=as.factor(sds[[4]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)
```

* Name: `cancer_firstage1990`
* Table name: `ubcosG1W4`
* Label: `Age of first diagnosis of cancer before the 1st November 1990`
* Description: 

```{r f142, echo=FALSE}
ssds <- data.frame(sds) #remove tibble format

ggplot(ssds[ssds[,4]==1,], aes(x=ssds[ssds[,4]==1,3],)) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

#### Harmonisation algorithm

For the variable `cancer`, value 0 is assigned when date of first diagnosis of cancer is later than 1st November 1990, the approximate date of the census registry, or never, and value 1 when prior to that date. 

**R script:**
```{r h141}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], cancer=sds[[4]])
```

For the variable `cancer_age`, the same age is assigned when the first diagnosis of cancer is before than 1st November 1990, otherwise the value 994 (not applicable) is assigned.

**R script:**
```{r h142}
# 'sds': study dataset
# 'hds': harmonised dataset
hds$cancer_age <- sds[[3]]
hds[hds$cancer != 1,]$cancer_age <- 994
```

#### Statistical description of the new harmonised variable
```{r d14, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)

hds[[3]] <- labelled(hds[[3]], labels = c_label_a)
ggplot(hds[hds[[3]]<990,], aes(x=hds[hds[[3]]<990,3])) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

<!---###### Validation
```{r v14, echo=FALSE}
#taux <- merge(hds, sds, by.x="id", by.y="athlosid")
#kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```
-->




<!--- ################## Save harmonised datasets ###################-->
```{r s14, echo=FALSE}
load("UBCoS_g1_w4.rdata")
UBCoS_g1_w4 <- full_join(UBCoS_g1_w4, hds, by="id", all=TRUE)
#save(UBCoS_g1_w4, file="UBCoS_g1_w4.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(hds[[2]], labels = m_label)
mds[[3]][mds[[3]] %in% c(991:999)] <- NA
val_labels(mds[[3]]) <- NULL
load("UBCoS_m_g1_w4.rdata")
UBCoS_m_g1_w4 <- full_join(UBCoS_m_g1_w4, mds, by="id", all=TRUE)
#save(UBCoS_m_g1_w4, file="UBCoS_m_g1_w4.rdata")

rm(list = c("hds", "sds", "mds"))
```

### Wave 5

#### Study-specific variable description

Two variables are taken from the UBCoS dataset:

* Name: `cancer2000`
* Table name: `ubcosG1W5`
* Description: `First diagnosis of cancer before the 1st November 2000`

```{r f151, echo=FALSE}
sds <- ubcosG1W5[c("athlosid", "cancer_firstdate2000", "cancer_firstage2000", "cancer2000")]

kable(frq(sds[[4]])[[1]])

ggplot(sds, aes(x=as.factor(sds[[4]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)
```

* Name: `cancer_firstage2000`
* Table name: `ubcosG1W5`
* Label: `Age of first diagnosis of cancer before the 1st November 2000`
* Description: 

```{r f152, echo=FALSE}
ssds <- data.frame(sds) #remove tibble format

ggplot(ssds[ssds[,4]==1,], aes(x=ssds[ssds[,4]==1,3],)) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

#### Harmonisation algorithm

For the variable `cancer`, value 0 is assigned when date of first diagnosis of cancer is later than 1st November 2000, the approximate date of the census registry, or never, and value 1 when prior to that date. 

**R script:**
```{r h151}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], cancer=sds[[4]])
```

For the variable `cancer_age`, the same age is assigned when the first diagnosis of cancer is before than 1st November 2000, otherwise the value 994 (not applicable) is assigned.

**R script:**
```{r h152}
# 'sds': study dataset
# 'hds': harmonised dataset
hds$cancer_age <- sds[[3]]
hds[hds$cancer != 1,]$cancer_age <- 994
```

#### Statistical description of the new harmonised variable
```{r d15, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)

hds[[3]] <- labelled(hds[[3]], labels = c_label_a)
ggplot(hds[hds[[3]]<990,], aes(x=hds[hds[[3]]<990,3])) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

<!---###### Validation
```{r v15, echo=FALSE}
#taux <- merge(hds, sds, by.x="id", by.y="athlosid")
#kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```
-->




<!--- ################## Save harmonised datasets ###################-->
```{r s15, echo=FALSE}
load("UBCoS_g1_w5.rdata")
UBCoS_g1_w5 <- full_join(UBCoS_g1_w5, hds, by="id", all=TRUE)
#save(UBCoS_g1_w5, file="UBCoS_g1_w5.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(hds[[2]], labels = m_label)
mds[[3]][mds[[3]] %in% c(991:999)] <- NA
val_labels(mds[[3]]) <- NULL
load("UBCoS_m_g1_w5.rdata")
UBCoS_m_g1_w5 <- full_join(UBCoS_m_g1_w5, mds, by="id", all=TRUE)
#save(UBCoS_m_g1_w5, file="UBCoS_m_g1_w5.rdata")

rm(list = c("hds", "sds", "mds"))
```


### Wave 6

#### Study-specific variable description

Two variables are taken from the UBCoS dataset:

* Name: `cancer2008`
* Table name: `ubcosG1W6`
* Description: `First diagnosis of cancer before the 1st November 2008`

```{r f161, echo=FALSE}
sds <- ubcosG1W6[c("athlosid", "cancer_firstdate2008", "cancer_firstage2008", "cancer2008")]

kable(frq(sds[[4]])[[1]])

ggplot(sds, aes(x=as.factor(sds[[4]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)
```

* Name: `cancer_firstage2008`
* Table name: `ubcosG1W6`
* Label: `Age of first diagnosis of cancer before the 1st November 2008`
* Description: 

```{r f162, echo=FALSE}
ssds <- data.frame(sds) #remove tibble format

ggplot(ssds[ssds[,4]==1,], aes(x=ssds[ssds[,4]==1,3],)) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

#### Harmonisation algorithm

For the variable `cancer`, value 0 is assigned when date of first diagnosis of cancer is later than 31st December 2008, the approximate date of the census registry, or never, and value 1 when prior to that date. 

**R script:**
```{r h161}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], cancer=sds[[4]])
```

For the variable `cancer_age`, the same age is assigned when the first diagnosis of cancer is before than 31st December 2008, otherwise the value 994 (not applicable) is assigned.

**R script:**
```{r h162}
# 'sds': study dataset
# 'hds': harmonised dataset
hds$cancer_age <- sds[[3]]
hds[hds$cancer != 1,]$cancer_age <- 994
```

#### Statistical description of the new harmonised variable
```{r d16, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)

hds[[3]] <- labelled(hds[[3]], labels = c_label_a)
ggplot(hds[hds[[3]]<990,], aes(x=hds[hds[[3]]<990,3])) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

<!---###### Validation
```{r v16, echo=FALSE}
#taux <- merge(hds, sds, by.x="id", by.y="athlosid")
#kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```
-->




<!--- ################## Save harmonised datasets ###################-->
```{r s16, echo=FALSE}
load("UBCoS_g1_w6.rdata")
UBCoS_g1_w6 <- full_join(UBCoS_g1_w6, hds, by="id", all=TRUE)
#save(UBCoS_g1_w6, file="UBCoS_g1_w6.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(hds[[2]], labels = m_label)
mds[[3]][mds[[3]] %in% c(991:999)] <- NA
val_labels(mds[[3]]) <- NULL
load("UBCoS_m_g1_w6.rdata")
UBCoS_m_g1_w6 <- full_join(UBCoS_m_g1_w6, mds, by="id", all=TRUE)
#save(UBCoS_m_g1_w6, file="UBCoS_m_g1_w6.rdata")

rm(list = c("hds", "sds", "mds"))
```



<!-- ###################################################################################################### -->
<!-- ###################################################################################################### --> 


## Uppsala 2nd generation cohort

### Wave 1

No information was registered.

### Wave 2

#### Study-specific variable description

Two variables are taken from the UBCoS dataset:

* Name: `cancer1970`
* Table name: `ubcosG2W2`
* Description: `First diagnosis of cancer before the 1st November 1970`

```{r f221, echo=FALSE}
sds <- ubcosG2W2[c("athlosid", "cancer_firstdate1970", "cancer_firstage1970", "cancer1970")]

kable(frq(sds[[4]])[[1]])

ggplot(sds, aes(x=as.factor(sds[[4]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)
```

* Name: `cancer_firstage1970`
* Table name: `ubcosG2W2`
* Label: `Age of first diagnosis of cancer before the 1st November 1970`
* Description: 

```{r f222, echo=FALSE}
ssds <- data.frame(sds) #remove tibble format

ggplot(ssds[ssds[,4]==1,], aes(x=ssds[ssds[,4]==1,3],)) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

#### Harmonisation algorithm

For the variable `cancer`, value 0 is assigned when date of first diagnosis of cancer is later than 1st November 1970, the approximate date of the census registry, or never, and value 1 when prior to that date. 

**R script:**
```{r h221}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], cancer=sds[[4]])
```

For the variable `cancer_age`, the same age is assigned when the first diagnosis of cancer is before than 1st November 1970, otherwise the value 994 (not applicable) is assigned.

**R script:**
```{r h222}
# 'sds': study dataset
# 'hds': harmonised dataset
hds$cancer_age <- sds[[3]]
hds[hds$cancer != 1,]$cancer_age <- 994
```

#### Statistical description of the new harmonised variable
```{r d22, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)

hds[[3]] <- labelled(hds[[3]], labels = c_label_a)
#ggplot(hds[hds[[3]]<990,], aes(x=hds[hds[[3]]<990,3])) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

<!---###### Validation
```{r v22, echo=FALSE}
#taux <- merge(hds, sds, by.x="id", by.y="athlosid")
#kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```
-->




<!--- ################## Save harmonised datasets ###################-->
```{r s22, echo=FALSE}
load("UBCoS_g2_w2.rdata")
UBCoS_g2_w2 <- full_join(UBCoS_g2_w2, hds, by="id", all=TRUE)
#save(UBCoS_g2_w2, file="UBCoS_g2_w2.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(hds[[2]], labels = m_label)
mds[[3]][mds[[3]] %in% c(991:999)] <- NA
val_labels(mds[[3]]) <- NULL
load("UBCoS_m_g2_w2.rdata")
UBCoS_m_g2_w2 <- full_join(UBCoS_m_g2_w2, mds, by="id", all=TRUE)
#save(UBCoS_m_g2_w2, file="UBCoS_m_g2_w2.rdata")

rm(list = c("hds", "sds", "mds"))
```

### Wave 3

#### Study-specific variable description

Two variables are taken from the UBCoS dataset:

* Name: `cancer1980`
* Table name: `ubcosG2W3`
* Description: `First diagnosis of cancer before the 15th September 1980`

```{r f231, echo=FALSE}
sds <- ubcosG2W3[c("athlosid", "cancer_firstdate1980", "cancer_firstage1980", "cancer1980")]

kable(frq(sds[[4]])[[1]])

ggplot(sds, aes(x=as.factor(sds[[4]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)
```

* Name: `cancer_firstage1980`
* Table name: `ubcosG2W3`
* Label: `Age of first diagnosis of cancer before the 15th September 1980`
* Description: 

```{r f232, echo=FALSE}
ssds <- data.frame(sds) #remove tibble format

ggplot(ssds[ssds[,4]==1,], aes(x=ssds[ssds[,4]==1,3],)) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

#### Harmonisation algorithm

For the variable `cancer`, value 0 is assigned when date of first diagnosis of cancer is later than 15th September 1980, the approximate date of the census registry, or never, and value 1 when prior to that date. 

**R script:**
```{r h231}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], cancer=sds[[4]])
```

For the variable `cancer_age`, the same age is assigned when the first diagnosis of cancer is before than 15th September 1980, otherwise the value 994 (not applicable) is assigned.

**R script:**
```{r h232}
# 'sds': study dataset
# 'hds': harmonised dataset
hds$cancer_age <- sds[[3]]
hds[hds$cancer != 1,]$cancer_age <- 994
```

#### Statistical description of the new harmonised variable
```{r d23, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)

hds[[3]] <- labelled(hds[[3]], labels = c_label_a)
ggplot(hds[hds[[3]]<990,], aes(x=hds[hds[[3]]<990,3])) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

<!---###### Validation
```{r v23, echo=FALSE}
#taux <- merge(hds, sds, by.x="id", by.y="athlosid")
#kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```
-->




<!--- ################## Save harmonised datasets ###################-->
```{r s23, echo=FALSE}
load("UBCoS_g2_w3.rdata")
UBCoS_g2_w3 <- full_join(UBCoS_g2_w3, hds, by="id", all=TRUE)
#save(UBCoS_g2_w3, file="UBCoS_g2_w3.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(hds[[2]], labels = m_label)
mds[[3]][mds[[3]] %in% c(991:999)] <- NA
val_labels(mds[[3]]) <- NULL
load("UBCoS_m_g2_w3.rdata")
UBCoS_m_g2_w3 <- full_join(UBCoS_m_g2_w3, mds, by="id", all=TRUE)
#save(UBCoS_m_g2_w3, file="UBCoS_m_g2_w3.rdata")

rm(list = c("hds", "sds", "mds"))
```

### Wave 4

#### Study-specific variable description

Two variables are taken from the UBCoS dataset:

* Name: `cancer1990`
* Table name: `ubcosG2W4`
* Description: `First diagnosis of cancer before the 1st November 1990`

```{r f241, echo=FALSE}
sds <- ubcosG2W4[c("athlosid", "cancer_firstdate1990", "cancer_firstage1990", "cancer1990")]

kable(frq(sds[[4]])[[1]])

ggplot(sds, aes(x=as.factor(sds[[4]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)
```

* Name: `cancer_firstage1990`
* Table name: `ubcosG2W4`
* Label: `Age of first diagnosis of cancer before the 1st November 1990`
* Description: 

```{r f242, echo=FALSE}
ssds <- data.frame(sds) #remove tibble format

ggplot(ssds[ssds[,4]==1,], aes(x=ssds[ssds[,4]==1,3],)) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

#### Harmonisation algorithm

For the variable `cancer`, value 0 is assigned when date of first diagnosis of cancer is later than 1st November 1990, the approximate date of the census registry, or never, and value 1 when prior to that date. 

**R script:**
```{r h241}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], cancer=sds[[4]])
```

For the variable `cancer_age`, the same age is assigned when the first diagnosis of cancer is before than 1st November 1990, otherwise the value 994 (not applicable) is assigned.

**R script:**
```{r h242}
# 'sds': study dataset
# 'hds': harmonised dataset
hds$cancer_age <- sds[[3]]
hds[hds$cancer != 1,]$cancer_age <- 994
```

#### Statistical description of the new harmonised variable
```{r d24, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)

hds[[3]] <- labelled(hds[[3]], labels = c_label_a)
ggplot(hds[hds[[3]]<990,], aes(x=hds[hds[[3]]<990,3])) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

<!---###### Validation
```{r v24, echo=FALSE}
#taux <- merge(hds, sds, by.x="id", by.y="athlosid")
#kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```
-->




<!--- ################## Save harmonised datasets ###################-->
```{r s24, echo=FALSE}
load("UBCoS_g2_w4.rdata")
UBCoS_g2_w4 <- full_join(UBCoS_g2_w4, hds, by="id", all=TRUE)
#save(UBCoS_g2_w4, file="UBCoS_g2_w4.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(hds[[2]], labels = m_label)
mds[[3]][mds[[3]] %in% c(991:999)] <- NA
val_labels(mds[[3]]) <- NULL
load("UBCoS_m_g2_w4.rdata")
UBCoS_m_g2_w4 <- full_join(UBCoS_m_g2_w4, mds, by="id", all=TRUE)
#save(UBCoS_m_g2_w4, file="UBCoS_m_g2_w4.rdata")

rm(list = c("hds", "sds", "mds"))
```

### Wave 5

#### Study-specific variable description

Two variables are taken from the UBCoS dataset:

* Name: `cancer2000`
* Table name: `ubcosG2W5`
* Description: `First diagnosis of cancer before the 1st November 2000`

```{r f251, echo=FALSE}
sds <- ubcosG2W5[c("athlosid", "cancer_firstdate2000", "cancer_firstage2000", "cancer2000")]

kable(frq(sds[[4]])[[1]])

ggplot(sds, aes(x=as.factor(sds[[4]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)
```

* Name: `cancer_firstage2000`
* Table name: `ubcosG2W5`
* Label: `Age of first diagnosis of cancer before the 1st November 2000`
* Description: 

```{r f252, echo=FALSE}
ssds <- data.frame(sds) #remove tibble format

ggplot(ssds[ssds[,4]==1,], aes(x=ssds[ssds[,4]==1,3],)) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

#### Harmonisation algorithm

For the variable `cancer`, value 0 is assigned when date of first diagnosis of cancer is later than 1st November 2000, the approximate date of the census registry, or never, and value 1 when prior to that date. 

**R script:**
```{r h251}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], cancer=sds[[4]])
```

For the variable `cancer_age`, the same age is assigned when the first diagnosis of cancer is before than 1st November 2000, otherwise the value 994 (not applicable) is assigned.

**R script:**
```{r h252}
# 'sds': study dataset
# 'hds': harmonised dataset
hds$cancer_age <- sds[[3]]
hds[hds$cancer != 1,]$cancer_age <- 994
```

#### Statistical description of the new harmonised variable
```{r d25, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)

hds[[3]] <- labelled(hds[[3]], labels = c_label_a)
ggplot(hds[hds[[3]]<990,], aes(x=hds[hds[[3]]<990,3])) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

<!---###### Validation
```{r v25, echo=FALSE}
#taux <- merge(hds, sds, by.x="id", by.y="athlosid")
#kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```
-->




<!--- ################## Save harmonised datasets ###################-->
```{r s25, echo=FALSE}
load("UBCoS_g2_w5.rdata")
UBCoS_g2_w5 <- full_join(UBCoS_g2_w5, hds, by="id", all=TRUE)
#save(UBCoS_g2_w5, file="UBCoS_g2_w5.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(hds[[2]], labels = m_label)
mds[[3]][mds[[3]] %in% c(991:999)] <- NA
val_labels(mds[[3]]) <- NULL
load("UBCoS_m_g2_w5.rdata")
UBCoS_m_g2_w5 <- full_join(UBCoS_m_g2_w5, mds, by="id", all=TRUE)
#save(UBCoS_m_g2_w5, file="UBCoS_m_g2_w5.rdata")

rm(list = c("hds", "sds", "mds"))
```


### Wave 6

#### Study-specific variable description

Two variables are taken from the UBCoS dataset:

* Name: `cancer2008`
* Table name: `ubcosG2W6`
* Description: `First diagnosis of cancer before the 1st November 2008`

```{r f261, echo=FALSE}
sds <- ubcosG2W6[c("athlosid", "cancer_firstdate2008", "cancer_firstage2008", "cancer2008")]

kable(frq(sds[[4]])[[1]])

ggplot(sds, aes(x=as.factor(sds[[4]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)
```

* Name: `cancer_firstage2008`
* Table name: `ubcosG2W6`
* Label: `Age of first diagnosis of cancer before the 1st November 2008`
* Description: 

```{r f262, echo=FALSE}
ssds <- data.frame(sds) #remove tibble format

ggplot(ssds[ssds[,4]==1,], aes(x=ssds[ssds[,4]==1,3],)) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

#### Harmonisation algorithm

For the variable `cancer`, value 0 is assigned when date of first diagnosis of cancer is later than 31st December 2008, the approximate date of the census registry, or never, and value 1 when prior to that date. 

**R script:**
```{r h261}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], cancer=sds[[4]])
```

For the variable `cancer_age`, the same age is assigned when the first diagnosis of cancer is before than 31st December 2008, otherwise the value 994 (not applicable) is assigned.

**R script:**
```{r h262}
# 'sds': study dataset
# 'hds': harmonised dataset
hds$cancer_age <- sds[[3]]
hds[hds$cancer != 1,]$cancer_age <- 994
```

#### Statistical description of the new harmonised variable
```{r d26, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent)

hds[[3]] <- labelled(hds[[3]], labels = c_label_a)
ggplot(hds[hds[[3]]<990,], aes(x=hds[hds[[3]]<990,3])) + geom_histogram(aes(), fill="steelblue", breaks=seq(30, 65, by =5), col="red") + xlab(ds_label_a)
```

<!---###### Validation
```{r v26, echo=FALSE}
#taux <- merge(hds, sds, by.x="id", by.y="athlosid")
#kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```
-->



<!--- ################## Save harmonised datasets ###################-->
```{r s26, echo=FALSE}
load("UBCoS_g2_w6.rdata")
UBCoS_g2_w6 <- full_join(UBCoS_g2_w6, hds, by="id", all=TRUE)
#save(UBCoS_g2_w6, file="UBCoS_g2_w6.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(hds[[2]], labels = m_label)
mds[[3]][mds[[3]] %in% c(991:999)] <- NA
val_labels(mds[[3]]) <- NULL
load("UBCoS_m_g2_w6.rdata")
UBCoS_m_g2_w6 <- full_join(UBCoS_m_g2_w6, mds, by="id", all=TRUE)
#save(UBCoS_m_g2_w6, file="UBCoS_m_g2_w6.rdata")

rm(list = c("hds", "sds", "mds"))
```




<!-- ########################################################## --> 
<!-- ########################################################## --> 
<!-- ########################################################## --> 


## Validation accross waves

The validation consists to check the variable accross waves. 

**R script**
```{r vv}
# For 1st generation:
list_df <- list(tibble(id= UBCoS_m_g1_w2$id, hdiab2=UBCoS_m_g1_w2$cancer, adiab2=UBCoS_m_g1_w2$cancer_age),
                tibble(id= UBCoS_m_g1_w3$id, hdiab3=UBCoS_m_g1_w3$cancer, adiab3=UBCoS_m_g1_w3$cancer_age), 
                tibble(id= UBCoS_m_g1_w4$id, hdiab4=UBCoS_m_g1_w4$cancer, adiab4=UBCoS_m_g1_w4$cancer_age),
                tibble(id= UBCoS_m_g1_w5$id, hdiab5=UBCoS_m_g1_w5$cancer, adiab5=UBCoS_m_g1_w5$cancer_age), 
                tibble(id= UBCoS_m_g1_w6$id, hdiab6=UBCoS_m_g1_w6$cancer, adiab6=UBCoS_m_g1_w6$cancer_age))
MyMerge <- function(x, y){
  df <- full_join(x, y, by= "id")
  return(df)
}
new.df <- Reduce(MyMerge, list_df)

v.ndf <- with(new.df, paste(hdiab2, hdiab3, hdiab4, hdiab5, hdiab6,sep=""))
kable(frq(v.ndf)[[1]][,c(1,2,4)])


f.ascending <- function(v) {  # return true or false
  return(all(diff(na.omit(v)) >= 0))
}

adiab <- as.matrix(new.df[, c("adiab2", "adiab3", "adiab4", "adiab5", "adiab6")])
tf <- apply(adiab, 1, f.ascending)
table(tf)


# For 2nd generation:**
list_df <- list(tibble(id= UBCoS_m_g2_w2$id, hdiab2=UBCoS_m_g2_w2$cancer, adiab2=UBCoS_m_g2_w2$cancer_age),
                tibble(id= UBCoS_m_g2_w3$id, hdiab3=UBCoS_m_g2_w3$cancer, adiab3=UBCoS_m_g2_w3$cancer_age), 
                tibble(id= UBCoS_m_g2_w4$id, hdiab4=UBCoS_m_g2_w4$cancer, adiab4=UBCoS_m_g2_w4$cancer_age),
                tibble(id= UBCoS_m_g2_w5$id, hdiab5=UBCoS_m_g2_w5$cancer, adiab5=UBCoS_m_g2_w5$cancer_age), 
                tibble(id= UBCoS_m_g2_w6$id, hdiab6=UBCoS_m_g2_w6$cancer, adiab6=UBCoS_m_g2_w6$cancer_age))

new.df <- Reduce(MyMerge, list_df)
v.ndf <- with(new.df, paste(hdiab2, hdiab3, hdiab4, hdiab5, hdiab6,sep=""))
kable(frq(v.ndf)[[1]][,c(1,2,4)])

adiab <- as.matrix(new.df[, c("adiab2", "adiab3", "adiab4", "adiab5", "adiab6")])
tf <- apply(adiab, 1, f.ascending)
table(tf)
```


# Quality estimation
[Comments on the quality of the new harmonised variable.]