---
title: "Marital Status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("setup_ubcos.r")
```
<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `marital_status`
* Variable label: `Marital_status`
* Variable description: `Participant's marital_status`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
1        | single
2        | married-cohabitating
3        | divorced-separated
4        | widow

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not applicable
995 | Does not answer
996 | Not attempt/not done
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Marital_status"
c_label  <- c("single"=1, "married-cohabitating"=2, "divorced-separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991)
m_label <- c("single"=1, "married-cohabitating"=2, "divorced-separated"=3, "widow"=4)
```

<!-- ########################################################## --> 

# Data process

## Uppsala 1st generation cohort

### Wave 1

#### Study-specific variable description

* Name: `marital_status`
* Label: `Marital_status of the individual registered`
* Table name: `ubcosG1W1`
* Description: 

```{r f11, echo=FALSE}
sds <- ubcosG1W1[,c("athlosid", "marital_status1960")]
sds[[2]] <- labelled(sds[[2]], labels = c_label)

kable(frq(sds[[2]])[[1]])
ggplot(sds, aes(x=as_factor(sds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))
```

#### Harmonisation algorithm

No changes.

**R script:**
```{r h11}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], marital_status=sds[[2]])
```

#### Statistical description of the new harmonised variable
```{r d11, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))
```

#### Validation
```{r v11, echo=FALSE}
taux <- merge(hds, sds, by.x="id", by.y="athlosid")
kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```




<!--- ################## Save harmonised datasets ###################-->
```{r s11, echo=FALSE}
load("UBCoS_g1_w1.rdata")
UBCoS_g1_w1 <- full_join(UBCoS_g1_w1, hds, by="id", all=TRUE)
#save(UBCoS_g1_w1, file="UBCoS_g1_w1.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(mds[[2]], labels = m_label)
load("UBCoS_m_g1_w1.rdata")
UBCoS_m_g1_w1 <- full_join(UBCoS_m_g1_w1, mds, by="id", all=TRUE)
#save(UBCoS_m_g1_w1, file="UBCoS_m_g1_w1.rdata")

rm(list = c("hds", "sds", "mds"))
```

### Wave 2

#### Study-specific variable description

* Name: `marital_status`
* Label: `Marital_status of the individual registered`
* Table name: `ubcosG1W2`
* Description: 

```{r f12, echo=FALSE}
sds <- ubcosG1W2[ , c("athlosid", "marital_status1970")]
sds[[2]] <- labelled(sds[[2]], labels = c_label)

kable(frq(sds[[2]])[[1]])
ggplot(sds, aes(x=as_factor(sds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))

```

#### Harmonisation algorithm

No changes.

**R script:**
```{r h12}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], marital_status=sds[[2]])
```

#### Statistical description of the new harmonised variable
```{r d12, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))
```

#### Validation
```{r v12, echo=FALSE}
taux <- merge(hds, sds, by.x="id", by.y="athlosid")
kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```

<!--- ################## Save harmonised datasets ###################-->
```{r s12, echo=FALSE}
load("UBCoS_g1_w2.rdata")
UBCoS_g1_w2 <- full_join(UBCoS_g1_w2, hds, by="id", all=TRUE)
#save(UBCoS_g1_w2, file="UBCoS_g1_w2.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(mds[[2]], labels = m_label)
load("UBCoS_m_g1_w2.rdata")
UBCoS_m_g1_w2 <- full_join(UBCoS_m_g1_w2, mds, by="id", all=TRUE)
#save(UBCoS_m_g1_w2, file="UBCoS_m_g1_w2.rdata")

rm(list = c("hds", "sds", "mds"))
```

### Wave 3

#### Study-specific variable description

* Name: `marital_status`
* Label: `Marital_status of the individual registered`
* Table name: `ubcosG1W3`
* Description: 

```{r f13, echo=FALSE}
sds <- ubcosG1W3[ , c("athlosid", "marital_status1980")]
sds[[2]] <- labelled(sds[[2]], labels = c_label)

kable(frq(sds[[2]])[[1]])
ggplot(sds, aes(x=as_factor(sds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))

```

#### Harmonisation algorithm

No changes.

**R script:**
```{r h13}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], marital_status=sds[[2]])
```

#### Statistical description of the new harmonised variable
```{r d13, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))
```

#### Validation
```{r v13, echo=FALSE}
taux <- merge(hds, sds, by.x="id", by.y="athlosid")
kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```




<!--- ################## Save harmonised datasets ###################-->
```{r s13, echo=FALSE}
load("UBCoS_g1_w3.rdata")
UBCoS_g1_w3 <- full_join(UBCoS_g1_w3, hds, by="id", all=TRUE)
#save(UBCoS_g1_w3, file="UBCoS_g1_w3.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(mds[[2]], labels = m_label)
load("UBCoS_m_g1_w3.rdata")
UBCoS_m_g1_w3 <- full_join(UBCoS_m_g1_w3, mds, by="id", all=TRUE)
#save(UBCoS_m_g1_w3, file="UBCoS_m_g1_w3.rdata")

rm(list = c("hds", "sds", "mds"))
```

### Wave 4

#### Study-specific variable description

* Name: `marital_status`
* Label: `Marital_status of the individual registered`
* Table name: `ubcosG1W4`
* Description: 

```{r f14, echo=FALSE}
sds <- ubcosG1W4[ , c("athlosid", "marital_status1990")]
sds[[2]] <- labelled(sds[[2]], labels = c_label)

kable(frq(sds[[2]])[[1]])
ggplot(sds, aes(x=as_factor(sds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))

```

#### Harmonisation algorithm

No changes.




**R script:**
```{r h14}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], marital_status=sds[[2]])
```

#### Statistical description of the new harmonised variable
```{r d14, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))
```

#### Validation
```{r v14, echo=FALSE}
taux <- merge(hds, sds, by.x="id", by.y="athlosid")
kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```




<!--- ################## Save harmonised datasets ###################-->
```{r s14, echo=FALSE}
load("UBCoS_g1_w4.rdata")
UBCoS_g1_w4 <- full_join(UBCoS_g1_w4, hds, by="id", all=TRUE)
#save(UBCoS_g1_w4, file="UBCoS_g1_w4.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(mds[[2]], labels = m_label)
load("UBCoS_m_g1_w4.rdata")
UBCoS_m_g1_w4 <- full_join(UBCoS_m_g1_w4, mds, by="id", all=TRUE)
#save(UBCoS_m_g1_w4, file="UBCoS_m_g1_w4.rdata")

rm(list = c("hds", "sds", "mds"))
```

### Wave 5

No data.

### Wave 6

No data.


<!-- ###################################################################################################### -->
<!-- ###################################################################################################### --> 


## Uppsala 2nd generation cohort

### Wave 1

#### Study-specific variable description

* Name: `marital_status`
* Label: `Marital_status of the individual registered`
* Table name: `ubcosG2W1`
* Description: 

```{r f21, echo=FALSE}
sds <- ubcosG2W1[, c("athlosid", "marital_status1960")]
sds[[2]] <- labelled(sds[[2]], labels = c_label)

kable(frq(sds[[2]])[[1]])
ggplot(sds, aes(x=as_factor(sds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))

```

#### Harmonisation algorithm

No changes.




**R script:**
```{r h21}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], marital_status=sds[[2]])
```

#### Statistical description of the new harmonised variable
```{r d21, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))
```

#### Validation
```{r v21, echo=FALSE}
taux <- merge(hds, sds, by.x="id", by.y="athlosid")
kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```




<!--- ################## Save harmonised datasets ###################-->
```{r s21, echo=FALSE}
load("UBCoS_g2_w1.rdata")
UBCoS_g2_w1 <- full_join(UBCoS_g2_w1, hds, by="id", all=TRUE)
#save(UBCoS_g2_w1, file="UBCoS_g2_w1.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(mds[[2]], labels = m_label)
load("UBCoS_m_g2_w1.rdata")
UBCoS_m_g2_w1 <- full_join(UBCoS_m_g2_w1, mds, by="id", all=TRUE)
#save(UBCoS_m_g2_w1, file="UBCoS_m_g2_w1.rdata")

rm(list = c("hds", "sds", "mds"))
```

### Wave 2

#### Study-specific variable description

* Name: `marital_status`
* Label: `Marital_status of the individual registered`
* Table name: `ubcosG2W2`
* Description: 

```{r f22, echo=FALSE}
sds <- ubcosG2W2[ , c("athlosid", "marital_status1970")]
sds[[2]] <- labelled(sds[[2]], labels = c_label)

kable(frq(sds[[2]])[[1]])
ggplot(sds, aes(x=as_factor(sds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))

```

#### Harmonisation algorithm

No changes.




**R script:**
```{r h22}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], marital_status=sds[[2]])
```

#### Statistical description of the new harmonised variable
```{r d22, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))
```

#### Validation
```{r v22, echo=FALSE}
taux <- merge(hds, sds, by.x="id", by.y="athlosid")
kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```




<!--- ################## Save harmonised datasets ###################-->
```{r s22, echo=FALSE}
load("UBCoS_g2_w2.rdata")
UBCoS_g2_w2 <- full_join(UBCoS_g2_w2, hds, by="id", all=TRUE)
#save(UBCoS_g2_w2, file="UBCoS_g2_w2.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(mds[[2]], labels = m_label)
load("UBCoS_m_g2_w2.rdata")
UBCoS_m_g2_w2 <- full_join(UBCoS_m_g2_w2, mds, by="id", all=TRUE)
#save(UBCoS_m_g2_w2, file="UBCoS_m_g2_w2.rdata")

rm(list = c("hds", "sds", "mds"))
```

### Wave 3

#### Study-specific variable description

* Name: `marital_status`
* Label: `Marital_status of the individual registered`
* Table name: `ubcosG2W3`
* Description: 

```{r f23, echo=FALSE}
sds <- ubcosG2W3[ , c("athlosid", "marital_status1980")]
sds[[2]] <- labelled(sds[[2]], labels = c_label)

kable(frq(sds[[2]])[[1]])
ggplot(sds, aes(x=as_factor(sds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))

```

#### Harmonisation algorithm

No changes.




**R script:**
```{r h23}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], marital_status=sds[[2]])
```

#### Statistical description of the new harmonised variable
```{r d23, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))
```

#### Validation
```{r v23, echo=FALSE}
taux <- merge(hds, sds, by.x="id", by.y="athlosid")
kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```




<!--- ################## Save harmonised datasets ###################-->
```{r s23, echo=FALSE}
load("UBCoS_g2_w3.rdata")
UBCoS_g2_w3 <- full_join(UBCoS_g2_w3, hds, by="id", all=TRUE)
#save(UBCoS_g2_w3, file="UBCoS_g2_w3.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(mds[[2]], labels = m_label)
load("UBCoS_m_g2_w3.rdata")
UBCoS_m_g2_w3 <- full_join(UBCoS_m_g2_w3, mds, by="id", all=TRUE)
#save(UBCoS_m_g2_w3, file="UBCoS_m_g2_w3.rdata")

rm(list = c("hds", "sds", "mds"))
```

### Wave 4

#### Study-specific variable description

* Name: `marital_status`
* Label: `Marital_status of the individual registered`
* Table name: `ubcosG2W4`
* Description: 

```{r f24, echo=FALSE}
sds <- ubcosG2W4[ , c("athlosid", "marital_status1990")]
sds[[2]] <- labelled(sds[[2]], labels = c_label)

kable(frq(sds[[2]])[[1]])
ggplot(sds, aes(x=as_factor(sds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))

```

#### Harmonisation algorithm

No changes.




**R script:**
```{r h24}
# 'sds': study dataset
# 'hds': harmonised dataset
hds <- tibble(id=sds[[1]], marital_status=sds[[2]])
```

#### Statistical description of the new harmonised variable
```{r d24, echo=FALSE}
hds[[2]] <- labelled(hds[[2]], labels = c_label)
kable(frq(hds[[2]])[[1]])
ggplot(hds, aes(x=as_factor(hds[[2]]))) + geom_bar(aes(y=(..count..)/sum(..count..)), width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Proportion") + geom_text(aes(y=((..count..)/sum(..count..)), label=scales::percent((..count..)/sum(..count..))), stat="count", vjust=-0.25) + scale_y_continuous(labels=percent) + theme(axis.text.x=element_text(angle=30, hjust=1))
```

#### Validation
```{r v24, echo=FALSE}
taux <- merge(hds, sds, by.x="id", by.y="athlosid")
kable(as.table(flat_table(taux, 2, 3, show.values=T)))
```


<!--- ################## Save harmonised datasets ###################-->
```{r s24, echo=FALSE}
load("UBCoS_g2_w4.rdata")
UBCoS_g2_w4 <- full_join(UBCoS_g2_w4, hds, by="id", all=TRUE)
#save(UBCoS_g2_w4, file="UBCoS_g2_w4.rdata")

mds <- hds
mds[[2]][mds[[2]] %in% c(991:999)] <- NA
mds[[2]] <- labelled(mds[[2]], labels = m_label)
load("UBCoS_m_g2_w4.rdata")
UBCoS_m_g2_w4 <- full_join(UBCoS_m_g2_w4, mds, by="id", all=TRUE)
#save(UBCoS_m_g2_w4, file="UBCoS_m_g2_w4.rdata")

rm(list = c("hds", "sds", "mds"))
```

### Wave 5

No data.

### Wave 6

No data.


<!-- ########################################################## --> 
<!-- ########################################################## --> 
<!-- ########################################################## --> 


## Validation accross waves

The validation consists of checking just the most frequent (>0.3%) trajectories of marital-status.

**R script**
```{r vv}
# For 1st generation:
list_df <- list(tibble(id= UBCoS_m_g1_w1$id, marital_status1=UBCoS_m_g1_w1$marital_status),
                tibble(id= UBCoS_m_g1_w2$id, marital_status2=UBCoS_m_g1_w2$marital_status),
                tibble(id= UBCoS_m_g1_w3$id, marital_status3=UBCoS_m_g1_w3$marital_status), 
                tibble(id= UBCoS_m_g1_w4$id, marital_status4=UBCoS_m_g1_w4$marital_status) )
MyMerge <- function(x, y){
  df <- full_join(x, y, by= "id")
  return(df)
}
new.df <- Reduce(MyMerge, list_df)

v.ndf <- with(new.df, paste(marital_status1, marital_status2, marital_status3, marital_status4,sep=""))
ff <- frq(v.ndf)[[1]][,c(1,2,4)]
ff <- ff[ff[,3]>=0.3,]
kable(ff[order(-ff$frq),])

# For 2nd generation:**
list_df <- list(tibble(id= UBCoS_m_g2_w1$id, marital_status1=UBCoS_m_g2_w1$marital_status), 
                tibble(id= UBCoS_m_g2_w2$id, marital_status2=UBCoS_m_g2_w2$marital_status),
                tibble(id= UBCoS_m_g2_w3$id, marital_status3=UBCoS_m_g2_w3$marital_status), 
                tibble(id= UBCoS_m_g2_w4$id, marital_status4=UBCoS_m_g2_w4$marital_status) )

new.df <- Reduce(MyMerge, list_df)

v.ndf <- with(new.df, paste(marital_status1, marital_status2, marital_status3, marital_status4,sep=""))
ff<- frq(v.ndf)[[1]][,c(1,2,4)]
ff <- ff[ff[,3]>=0.3,]
kable(ff[order(-ff$frq),])
```


# Quality estimation
[Comments on the quality of the new harmonised variable.]
